---
title: "RStudio Walkthrough"
author: "Jim Clemens"
date: "June 10, 2015"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = TRUE, include = TRUE, echo = TRUE)
```

## RStudio: Making R Awesome

### Our mission: Give analysts working in R tools to be more productive and effective
<br>

### 70% of our R&D investments are in open source products
<br>

### Our Professional products fund our development activities

## RStudio Products
- RStudio IDE
- Shiny
- RMarkdown
- R Packages
- Professional Products

## RStudio IDE

### Version 0.99 now out!

- Overhaul of auto-complete
- New data viewer
- Code diagnostics in the editor
- Cusomizable code snippets
- Rcpp tools
- Several other improvements

## RStudio IDE (cont'd)

### Projects

- Allows you to create multiple contexts (working directory, workspace, history, and source docs)
<br>

### Integrated support for Git and Subversion
<br>

### Available Server Based

- Access via web browser
- Move computation closer to the data
- Reduce data loading latency
- Scale compute and RAM centrally
<br>

## Shiny - Easy web applications in R

- Open source R package
- Turn analyses into interactive web apps
- No HTML, CSS, or JavaScript knowledge needed
- Allows you to anticipate refinements
- You select the variables
- No more re-run, download, cut & paste process
- Reduces iteration and improves insight

## A Simple Shiny App
Number of obs:
```{r echo = TRUE, eval = FALSE}
numericInput("n", "",50)
```
See the plot:
```{r echo = TRUE, eval = FALSE}
renderPlot({
    hist(runif(input$n))
  })
```
----
Number of obs:
```{r echo = FALSE, eval = TRUE}
numericInput("n", "",50)
```
See the plot:
```{r echo = FALSE, eval = TRUE}
renderPlot({
    hist(runif(input$n))
  })
```


## Shiny Examples

[kmeans](http://shiny.rstudio.com/gallery/kmeans-example.html)

[Streaming Download Monitor](https://gallery.shinyapps.io/087-crandash)

[Movie Explorer](http://shiny.rstudio.com/gallery/movie-explorer.html)

[Superzip](http://shiny.rstudio.com/gallery/superzip-example.html)

## htmlwidgets

### JavaScript data visualization libraries available in R

- Numerous bindings available (ex: d3)
- New bindings being created by community
- Instructions for building bindings on the site

[htmlwidgets](http://www.htmlwidgets.org/)

### RMarkdown

- Simple report and documentation creation
- Embedded R code - source and output
- Makes data preparation and analyses fully reproducible
- Re-running source updates output with current values
- Supports HTML, pdf, Word, beamer and ioslides output
- This presentation is RMarkdown!

### R Packages

- dplyr
- ggplot2
- ggvis (interactive, next generation of ggplot2)
- packrat (dependency management)
- several others

### Professional Products

- 

## R Output

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
