---
title: "RStudio Walkthrough"
author: "Jim Clemens"
date: "June 10, 2015"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = TRUE, include = TRUE, echo = TRUE)
```

## **RStudio: Making R Awesome**

### **Our mission:** Give analysts working in R tools to be more productive and effective
<br>

### 70% of our R&D investments are in open source products
<br>

### Our Professional products fund our development activities

## RStudio Products
- RStudio IDE
- Shiny
- RMarkdown
- R Packages
- Professional Products

## RStudio IDE

### Version 0.99 now out!

- Overhaul of auto-complete
- New data viewer
- Code diagnostics in the editor
- Cusomizable code snippets
- Rcpp tools
- Several other improvements

## RStudio IDE (cont'd)

### Projects

- Allows you to create multiple contexts (working directory, workspace, history, and source docs)
<br>

### Integrated support for Git and Subversion
<br>

### Available Server Based

- Access via web browser
- Move computation closer to the data
- Reduce data loading latency
- Scale compute and RAM centrally
<br>

## Shiny - Easy web applications in R

- Open source R package
- Turn analyses into interactive web apps
- No HTML, CSS, or JavaScript knowledge needed
- Allows you to anticipate refinements
- You select the variables
- No more re-run, download, cut & paste process
- Reduces iteration and improves insight

## A Simple Shiny App
Number of obs:
```{r echo = TRUE, eval = FALSE}
numericInput("n", "",50)
```
See the plot:
```{r echo = TRUE, eval = FALSE}
renderPlot({
    hist(runif(input$n))
  })
```
----
Number of obs:
```{r echo = FALSE, eval = TRUE}
numericInput("n", "",50)
```
See the plot:
```{r echo = FALSE, eval = TRUE}
renderPlot({
    hist(runif(input$n))
  })
```


## Shiny Examples

[kmeans](http://shiny.rstudio.com/gallery/kmeans-example.html)

[Streaming Download Monitor](https://gallery.shinyapps.io/087-crandash)

[Movie Explorer](http://shiny.rstudio.com/gallery/movie-explorer.html)

[Superzip](http://shiny.rstudio.com/gallery/superzip-example.html)

## htmlwidgets

### JavaScript data visualization libraries available in R

- Numerous bindings available (ex: d3)
- New bindings being created by community
- Instructions for building bindings on the site

[htmlwidgets](http://www.htmlwidgets.org/)

## RMarkdown

- Simple report and documentation creation
- Embedded R code - source and output
- Makes data preparation and analyses fully reproducible
- Re-running source updates output with current values
- Supports HTML, pdf, Word, beamer and ioslides output
- This presentation was produced with RMarkdown!

[RMarkdown](http://rmarkdown.rstudio.com/)

## R Packages

- dplyr
- ggplot2
- ggvis (interactive, next generation of ggplot2)
- packrat (dependency management)
- several others

[R Packages](http://www.rstudio.com/products/rpackages/)

## Professional Products - RStudio Server Pro

### Added capabilities for corporate deployments
- Authentication (AD, LDAP, PAM)
- Enhanced ecurity
- Resource allocation (global, group and user)
- Advanced resource management (profiles, databases, versions, packages, CPU, etc.)
- Load balancing
- Performance monitoring
- RStudio support

[RStudio Comparison](http://www.rstudio.com/products/rstudio/)

## Professional Products - Shiny Server Pro

- Authentication (AD, LDAP, PAM)
- Multiple R processes per application
- Enhanced security
- Application concurrency limits
- Appoication and system erformance monitoring
- RStudio support

[Shiny Comparison](http://www.rstudio.com/products/shiny/shiny-server/)

### *Professional products fund all our development!*

